Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-07 manuscript/manuscript.Rmd
mini change

Mathematically, RL may be formulated using a discrete time *partially observable Markov decision process (POMDP)*.
This formalization is rather flexible and allows one, e.g., to account for situations where the agent may not fully observe the environment state, or where the only observations available to the agent are certain functions of the underlying state.
For the sake of clarity, we will present here only the class of POMDPs which are relevant to our work: fully observed POMDPs with trivial emission function (FMDPs for short).
An FMDP may be defined by the following data:
- $\mathcal{S}$: *state space*, the set of states of the environment,
- $\mathcal{A}$: *action space*, the set of actions which the agent may choose from,
- $T(s_{t+1}|s_t, a_t)$: *transition operator*, a conditional distribution which describes the dynamics of the system,
- $r(s_t, a_t)$: *reward function*, the reward obtained after performing action $a_t\in\mathcal{A}$ in state $s_t$,
- $d(s_0)$: *initial state distribution*, the initial state of the environment is sampled from this distribution,
- $\gamma\in[0,1]$: *discount factor*.

>>>>

Mathematically, RL may be formulated using a discrete time *partially observable Markov decision process (POMDP)*.
This formalization is rather flexible and allows one, e.g., to account for situations where the agent may not fully observe the environment state, or where the only observations available to the agent are certain functions of the underlying state.
For the sake of clarity, we will present here only the class of POMDPs which are relevant to our work: fully observed POMDPs with trivial emission function (FMDPs for short).
An FMDP may be defined by the following data:

- $\mathcal{S}$: *state space*, the set of states of the environment,

- $\mathcal{A}$: *action space*, the set of actions which the agent may choose from,

- $T(s_{t+1}|s_t, a_t)$: *transition operator*, a conditional distribution which describes the dynamics of the system,

- $r(s_t, a_t)$: *reward function*, the reward obtained after performing action $a_t\in\mathcal{A}$ in state $s_t$,

- $d(s_0)$: *initial state distribution*, the initial state of the environment is sampled from this distribution,

- $\gamma\in[0,1]$: *discount factor*.
